
\begin{thebibliography}{30}

    \bibitem{marek2023} Marek, D., Paszkuta, M., Szyguła, J. (2023). General Concepts in Swarm of Drones Control: Analysis and Implementation. \textit{2023 IEEE International Conference on Big Data (BigData)}. \url{https://doi.org/10.1109/BigData59044.2023.10386672}.
  
    \bibitem{bene2023} Bene, V., Kristóf, Z., \& Elek, B. (2023). The DJI Dock 2 "Drone in a Box" to Enhance the Unmanned Guard Solution. \textit{Repüléstudományi Közlemények}, 35(3), 171-181. \url{https://doi.org/10.32560/rk.2023.3.11}.
   
    \bibitem{desilva2022} De Silva, S. C., Phlernjai, M., Rianmora, S., \& Ratsamee, P. (2022). Inverted Docking Station: A Conceptual Design for a Battery-Swapping Platform for Quadrotor UAVs. \textit{Drones}, 6(3), 56. \url{https://doi.org/10.3390/drones6030056}.

    \bibitem{ardupilot}
    ArduPilot Documentation, ``Multicopter Overview,'' Disponible en: \url{https://ardupilot.org/copter/docs/common-multicopter-overview.html}. [\textit{Último acceso: noviembre, 2024}].


    
    \bibitem{piotr_drones}
    Piotr, W., et al., ``Drones or Unmanned Aerial Systems (UAV - Unmanned Aerial Vehicle or UAS - Unmanned Aerial Systems),'' \textit{Introduction to UAV Systems}, Wiley, 2016, pp. 25--50. Disponible en: \url{https://doi.org/10.1002/9781118899893}.

    



    \bibitem{ardupilot_docs} ArduPilot Documentation, ``ArduPilot firmware works on a wide variety of different hardware to control unmanned vehicles of all types.'' Disponible en: \url{https://ardupilot.org/ardupilot/index.html}.


    \bibitem{lipo_batteries}
    Chen, L., ``Advances in Lithium Polymer Batteries for UAVs,'' \textit{Journal of Power Sources}, vol. 360, 2021, pp. 123--140. DOI: \url{https://doi.org/10.1016/j.jpowsour.2021.230917}.




    \bibitem{aplications_drones}
    DJI, ``Aplicaciones en la industria agrícola,'' Disponible en: \url{https://ag.dji.com/es}. [\textit{Último acceso: noviembre, 2024}].

    \bibitem{swarm_industrial}
    Bacco, M., et al., ``Drone Swarms in Industry 4.0: Potential and Challenges,'' \textit{IEEE Transactions on Industrial Informatics}, vol. 15, no. 12, 2019, pp. 6116--6125. DOI: \url{https://doi.org/10.1109/TII.2019.2904121}.


    \bibitem{swarming_drones}
    Marek, D., Paszkuta, M., Szyguła, J., Biernacki, P., Domanski, A., Szczygieł, M., Krol, M., Wojciechowski, K., ``General concepts in swarm of drones control: Analysis and implementation,'' \textit{2023 IEEE International Conference on Big Data (BigData)}, 2023, pp. 5070--5077. DOI: \url{https://doi.org/10.1109/BigData52589.2023.10386672}.



    \bibitem{grlj_docking_stations} 
    Grlj, C. G., Krznar, N. ``A decade of UAV docking stations: A brief overview of mobile and fixed landing platforms,'' \textit{Drones}, vol. 6, no. 1, 2022, p. 17. DOI: \url{https://doi.org/10.3390/drones6010017}.

%%ELECTRONICS SOA
    

    \bibitem{rohdE_ESC}
    Rohde , Schwarz, ``Optimizing ESC Design: Insights into Efficient Electronic Speed Controllers for Drones,'' Technical Whitepaper, 2020. Disponible en: \url{https://www.rohde-schwarz.com}. [\textit{Último acceso: noviembre, 2024}].

    \bibitem{flight_controllers}
    N. C. Ajay Vishwath, Arvind R. Yadav, Vishwes Mehra, Vijay Patel, Mansha Kumari B. Patel, Viral Sondagar, Aditi Sharma, Gurbhej Singh. (2024). Computational analysis and designing of flight controllers to improve drone performance. \textit{International Journal on Interactive Design and Manufacturing (IJIDeM)}. \url{https://doi.org/10.1007/s12008-024-02161-x}.

    \bibitem{pixhawk_docs}
    Pixhawk Development Team, ``Pixhawk Autopilot Platform,'' 2023. Disponible en: \url{https://docs.px4.io/}. [\textit{Último acceso: noviembre, 2024}].

    \bibitem{rasp_docs}
    Raspberry Pi Foundation, ``Raspberry Pi Documentation,'' Disponible en: \url{https://www.raspberrypi.com/documentation/}. [\textit{Último acceso: noviembre, 2024}].

    \bibitem{Gupta2019}
    Gupta, A., ``UART Communication,'' \textit{The IoT Hacker's Handbook: A Practical Guide to Hacking the Internet of Things}, Apress, Berkeley, CA, 2019, pp. 59--80. DOI: \url{https://doi.org/10.1007/978-1-4842-4300-8_4}.

    \bibitem{Wootton2016}
    Wootton, C., ``Serial Peripheral Interface (SPI),'' \textit{Samsung ARTIK Reference: The Definitive Developers Guide}, Apress, Berkeley, CA, 2016, pp. 335--349. DOI: \url{https://doi.org/10.1007/978-1-4842-2322-2_21}.

    \bibitem{Gazi2021}
    Gazi, O. and Arlı, A. Ç., ``Inter Integrated Circuit (I2C) Serial Communication in VHDL,'' \textit{State Machines using VHDL: FPGA Implementation of Serial Communication and Display Protocols}, Springer International Publishing, Cham, 2021, pp. 193--235. DOI: \url{https://doi.org/10.1007/978-3-030-61698-4_5}.

    \bibitem{CompComms2023}
    Chen, J. and Huang, S., ``Analysis and Comparison of UART, SPI and I2C,'' \textit{2023 IEEE 2nd International Conference on Electrical Engineering, Big Data and Algorithms (EEBDA)}, 2023, pp. 272--276. DOI: \url{https://doi.org/10.1109/EEBDA56825.2023.10090677}.

    \bibitem{fastchargers}
    Neaimeh, M., Salisbury, S. D., Hill, G. A., Blythe, P. T., Scoffield, D. R., Francfort, J. E., ``Analysing the usage and evidencing the importance of fast chargers for the adoption of battery electric vehicles,'' \textit{Energy Policy}, vol. 108, pp. 474-486, 2017. DOI: \url{https://doi.org/10.1016/j.enpol.2017.06.033}.

    \bibitem{vehiclessmartcharge}
    Sadeghian, O., et al., ``A comprehensive review on electric vehicles smart charging: Solutions, strategies, technologies, and challenges,'' \textit{Journal of Energy Storage}, vol. 54, 2022, pp. 105241. DOI: \url{https://doi.org/10.1016/j.est.2022.105241}.

    \bibitem{wiredvwirelessMohammed}
    Mohammed, S. A. Q., and Jung, J. W., ``A Comprehensive State-of-the-Art Review of Wired/Wireless Charging Technologies for Battery Electric Vehicles: Classification/Common Topologies/Future Research Issues,'' \textit{IEEE Access}, vol. 9, 2021, pp. 19572--19585. DOI: \url{https://doi.org/10.1109/ACCESS.2021.3055027}.

    \bibitem{wirelessLu}
    Lu, X., et al., ``Wireless Charging Technologies: Fundamentals, Standards, and Network Applications,'' \textit{IEEE Communications Surveys \& Tutorials}, vol. 18, no. 2, 2016, pp. 1413--1452. DOI: \url{https://doi.org/10.1109/COMST.2015.2499783}.


    %%software

    \bibitem{iso_firmware} ISO/IEC/IEEE 24765:2017, ``Systems and Software Engineering Vocabulary,'' International Organization for Standardization, 2017.
    \bibitem{px4_docs} PX4 Documentation, ``PX4 is a powerful open source autopilot flight stack running on the NuttX RTOS.'' Disponible en: \url{}.

    \bibitem{qgc_docs} QGroundControl Documentation, ``QGroundControl provides full flight control and vehicle setup for PX4 or ArduPilot powered vehicles.'' Disponible en: \url{https://docs.qgroundcontrol.com/en/}. 
    \bibitem{ubuntu_docs} Ubuntu Documentation, ``Designed for security, reliability, and ease of use.'' Disponible en: \url{https://ubuntu.com}. 
    \bibitem{raspbian_docs} Raspberry Pi OS Documentation, ``A Debian-based operating system specifically tuned for the Raspberry Pi hardware.'' Disponible en: \url{https://www.raspberrypi.org/documentation/raspbian/}.
    \bibitem{ros_docs} ROS 2 Documentation, ``Benefits and architecture of ROS 2 for distributed systems in robotics.'' Disponible en: \url{https://docs.ros.org/en/}. 
    \bibitem{humble_documentation}
    ROS 2 Documentation, ``Humble Hawksbill (LTS) Overview,'' Disponible en: \url{https://docs.ros.org/en/humble/}. [\textit{Último acceso: noviembre, 2024}].
    \bibitem{jazzy_documentation}
    ROS 2 Documentation, ``Jazzy Jalisco Overview,'' Disponible en: \url{https://docs.ros.org/en/jazzy/}. [\textit{Último acceso: noviembre, 2024}].
  % here 
  \bibitem{opencv_docs} OpenCV Documentation, ``An open-source computer vision and machine learning software library containing more than 2500 optimized algorithms.'' Disponible en: \url{https://docs.opencv.org/}. 

   
   
    \bibitem{opencv_calib3d}
    OpenCV Documentation, ``Camera Calibration and 3D Reconstruction (calib3d module),'' Disponible en: \url{https://docs.opencv.org/4.x/d9/d0c/group__calib3d.html}.
    \bibitem{aruco_docs} ArUco Documentation, ``ArUco is an OpenSource library for detecting squared fiducial markers in images.'' Disponible en: \url{}. 
    \bibitem{aruco_docs_pdf}
    Garrido-Jurado, S., et al., ``Automatic generation and detection of highly reliable fiducial markers under occlusion,'' \textit{Pattern Recognition}, 2014. DOI: \url{https://doi.org/10.1016/j.patcog.2014.01.005}.
    \bibitem{khazetdinov2021} Khazetdinov, M., et al., ``Embedded ArUco Markers for UAV Landing: High Accuracy Detection in Wide Distance Range,'' 2021. DOI: [DOI number or URL if available].
    \bibitem{opencv_docs_aruco}
    OpenCV Documentation, ``Detection of ArUco Markers,'' Disponible en: \url{https://docs.opencv.org/4.x/d5/dae/tutorial_aruco_detection.html}. [\textit{Último acceso: noviembre, 2024}].
    \bibitem{opencv_tutorial_aruco}
    OpenCV Documentation, ``ArUco Marker Detection: Example Tutorial,'' Disponible en: \url{https://docs.opencv.org/4.x/dc/dc3/tutorial_aruco_detection.html}. [\textit{Último acceso: noviembre, 2024}].
    \bibitem{mavlink_docs}
    MAVLink Documentation, ``Protocol Overview,'' Disponible en: \url{https://mavlink.io/en/}. [\textit{Último acceso: noviembre, 2024}].
    \bibitem{px4_ros2}
    PX4 and ROS Integration, ``Using MAVROS and Micro XRCE-DDS with ROS 2,'' Disponible en: \url{https://docs.px4.io/en/ros2/}. [\textit{Último acceso: noviembre, 2024}].

    \bibitem{gps_reference}
    GPS y RTK-GPS en sistemas de navegación para drones. Disponible en cualquier documentación técnica sobre GPS para drones, como los recursos de fabricantes (ej. Pixhawk o ArduPilot).
    \bibitem{non_gps_navigation}
        \textit{Non-GPS Navigation for ArduPilot.} Disponible en: \url{https://ardupilot.org/copter/docs/common-non-gps-navigation-landing-page.html}








   
   
    
  
   
   
    \bibitem{Subero2024}
    Subero, A., ``USART, SPI, I2C, and Communication Protocols,'' \textit{Programming PIC Microcontrollers with XC8: Mastering Classical Embedded Design}, Apress, Berkeley, CA, 2024, pp. 297--366. DOI: \url{https://doi.org/10.1007/979-8-8688-0467-0_8}.

    
   
    \bibitem{amazon_prime_air}
    Amazon Prime Air, ``Preparativos para entregas de paquetes con drones,'' Disponible en: \url{https://www.aboutamazon.com/news/transportation/amazon-prime-air-prepares-for-drone-deliveries}. [\textit{Último acceso: noviembre, 2024}].
    
    
    \bibitem{military_swarm_drones}
    Military Africa, ``Swarm drones: A new phase in the Sudan conflict,'' Disponible en: \url{https://www.military.africa/2024/10/swarm-drones-a-new-phase-in-the-sudan-conflict/}. [\textit{Último acceso: noviembre, 2024}].

   
  
  
    \bibitem{charging_stations_review}
    Zhao, Z., et al., ``Survey on Drone Charging Stations: Methods and Designs,'' \textit{Drones}, vol. 5, no. 2, 2021, pp. 50--62. DOI: \url{https://doi.org/10.3390/drones5020050}.

    \bibitem{drone_motors}
    Anaya, C., ``Understanding Brushless Motors for Drones,'' \textit{Drone Electronics: A Guide}, Springer, 2020, pp. 35--55. DOI: \url{https://doi.org/10.1007/978-3-030-41326-2}.

    \bibitem{drone_propellers}
    Vetelino, J., ``Design and Selection of Propellers for UAVs,'' \textit{Introduction to Drone Engineering}, CRC Press, 2018, pp. 145--170. Disponible en: \url{https://www.crcpress.com}.

   

    \bibitem{nieuwoudt2023} Nieuwoudt, H., Welgemoed, J., \& van Niekerk, T. (2023). Automated Charging and Docking Station for Security UAVs. \textit{2023 14th International Conference on Mechanical and Intelligent Manufacturing Technologies}. \url{https://doi.org/10.1109/ICMIMT59138.2023.10200192}.
    \bibitem{jiang2019} Jiang, Z. (2019). \textit{An Autonomous Landing and Charging System for Drones}. Master's Thesis, Massachusetts Institute of Technology.
    \bibitem{desilva2023} De Silva, S. C., \& Phlernjai, M. (2023). Development and Evaluation of Inverted Docking Station for Small Quadrotor UAV. \textit{2023 IEEE International Conference on Mechatronics and Automation}. \url{https://doi.org/10.1109/ICMA57826.2023.10215697}.
    
    

\end{thebibliography}

